Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-22 Papers/ms.tex
Two sentences
Talking a bit about results

@@

\subsection{Reproducibility of the results}
The ``effective sample size'' returned by DNest, which we have described as the
number of posterior samples, takes into account the fact DNest's target
distribution is not the posterior. However, it does not take autocorrelation
into account, and thus can present an optimistic picture of the accuracy of
any Monte Carlo approximations to posterior quantities. Most standard diagnostic
techniques used in MCMC can be applied here. The simplest of these is a
check of reproducibility. If different runs yield substantially different
results, the MCMC output should be treated with caution. For example, in
Figure~\ref{fig:masses2}, there is a correlation between the mass attributed
to the SIE component and that attributed to substructures. However, the
distribution also appears somewhat ``lumpy'' or multimodal. This is probably
not a feature of the actual posterior distribution, but rather appears due to
imperfect sampling. Whereas a standard Metropolis sampler would move around
very slowly in the hypothesis space, the DNS algorithm naturally spends some
of the time sampling the prior. Therefore, a particle exploring the parameter
space can ``forget'' its good fitting position, move somewhere completely
different, and find another good fitting model in a different location. This
is a natural feature of the algorithm (and is also present in related
algorithms such as parallel tempering). Despite this feature, the patchy
nature of Figure~\ref{fig:masses2} suggests that posterior exploration is
still challenging in this problem.

>>>>

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). The posterior distribution for
$N_{\rm lens}$ also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

@@

\subsection{Reproducibility of the results}\label{sec:convergence}
The ``effective sample size'' returned by DNest, which we have described as the
number of posterior samples, takes into account the fact DNest's target
distribution is not the posterior. However, it does not take autocorrelation
into account, and thus can present an optimistic picture of the accuracy of
any Monte Carlo approximations to posterior quantities. Most standard diagnostic
techniques used in MCMC can be applied here. The simplest of these is a
check of reproducibility. If different runs yield substantially different
results, the MCMC output should be treated with caution. For example, in
Figure~\ref{fig:masses2}, there is a correlation between the mass attributed
to the SIE component and that attributed to substructures. However, the
distribution also appears somewhat ``lumpy'' or multimodal. This is probably
not a feature of the actual posterior distribution, but rather appears due to
imperfect sampling. Whereas a standard Metropolis sampler would move around
very slowly in the hypothesis space, the DNS algorithm naturally spends some
of the time sampling the prior. Therefore, a particle exploring the parameter
space can ``forget'' its good fitting position, move somewhere completely
different, and find another good fitting model in a different location. This
is a natural feature of the algorithm (and is also present in related
algorithms such as parallel tempering). Despite this feature, the patchy
nature of Figure~\ref{fig:masses2} suggests that posterior exploration is
still challenging in this problem.
